\documentclass[letterpaper,11pt]{article}
\usepackage{fontawesome5}
\usepackage[utf8]{inputenc}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{setspace}
\renewcommand{\baselinestretch}{0.92}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.5in}
\setlength{\footskip}{4.08003pt}
\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-9pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1
\setstretch{0.5}

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item \small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{0pt}\item[]
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7.3pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item[]
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeItemListStart}{
  \begin{itemize}[leftmargin=0.3in, label=\textbullet]
  \setlength{\itemsep}{2pt}  
  \setlength{\parsep}{1pt}
}

\newcommand{\resumeItemListEnd}{
  \end{itemize}\vspace{-5pt}
}

%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{center}
    \textbf{\Huge  Daniel Park} \\ \vspace{2pt}
    \footnotesize +1(548)-788-1341 $|$ \href{mailto:parkdaniel0225@gmail.com}{\textcolor{blue}{\underline{parkdaniel0225@gmail.com}}} $|$ 
    \href{https://github.com/parkdaniel0225}{\textcolor{blue}{\underline{github.com/parkdaniel0225}}}
$|$ 
\href{https://www.linkedin.com/in/danielpark0225}{\textcolor{blue}{\underline{linkedin.com/in/danielpark0225}}}
$|$ 
\href{https://danielpark.vercel.app}{\textcolor{blue}{\underline{danielpark.vercel.app}}}
    
\end{center}

%-----------EDUCATION-----------
\vspace{-11pt}\section{\textcolor{blue}{\textbf{Education}}}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Western University}{Sept. 2021 -- Apr. 2026}
      {Specialization in \textbf{Computer Science}}{}
    \resumeItemListStart
\resumeItem{Member of \textbf{Western AI}, \textbf{Western CS Undergraduate Society} and Events Assistant at Western Sneaker Club.}
    \resumeItemListEnd
    \vspace{-6pt}\item \small{\textbf{Relevant Courses:} Machine Learning, Databases, Statistical Programming, Unstructured Data, Operating Systems, Data Structures and Algorithms, Computer Networks}
  \resumeSubHeadingListEnd

%---------------------Experience---------------
\section{\textcolor{blue}{\textbf{Professional Experiences}}}
\resumeSubHeadingListStart

\resumeSubheading
  {Data \& Machine Learning Intern}{Sept. 2025 -- Apr. 2026}
  {HEAL}{}
\resumeItemListStart
\resumeItem{Architected an automated, cloud-native \textbf{ETL pipeline} on \textbf{AWS} utilizing \textbf{Apache Airflow} to orchestrate data ingestion from the \textbf{Google Places API}, detecting spatial anomalies and ensuring cross-system integrity for downstream \textbf{machine learning (ML)} applications.}
\resumeItem{Developed robust \textbf{data transformation} micro-workflows in \textbf{Python (pandas, NumPy, regex)} to sanitize and reconcile unstructured text data, significantly reducing anomalies and decoupling data preparation from analytics flows.}
\resumeItem{Designed a scalable, version-controlled \textbf{data model} and storage architecture on \textbf{AWS} with rigorous schema validation, establishing centralized governance protocols that guaranteed high availability and long-term pipeline reliability.}
\resumeItem{Deployed predictive \textbf{machine learning models} utilizing \textbf{Scikit-Learn} and \textbf{XGBoost} (clustering, time-series forecasting) to analyze retail density trends, translating complex data into actionable visualizations to drive \textbf{strategic, data-driven decisions}.}
\resumeItem{Implemented \textbf{MLOps} best practices for model validation and performance monitoring, collaborating with \textbf{cross-functional stakeholders} to translate complex analytical outputs into clear technical specifications and business requirements.}
\resumeItemListEnd

\resumeSubheading
  {Data Science Intern}{Sept. 2024 -- Aug. 2025}
  {interRAI}{}
\resumeItemListStart
\resumeItem{Managed the end-to-end \textbf{ETL} and data preparation lifecycle for high-volume clinical datasets using \textbf{PySpark}, optimizing distributed validation processes to ensure high-fidelity inputs for advanced health research.}
\resumeItem{\textbf{Modernized} legacy data processing flows into automated, distributed workloads utilizing \textbf{Spark SQL}, reducing manual processing overhead and accelerating execution runtimes by approximately \textbf{30\%} for large-scale analysis.}
\resumeItem{Spearheaded a comprehensive technical training initiative and documented core \textbf{Spark} architectures, accelerating team onboarding and enabling unified \textbf{cross-functional collaboration} across multidisciplinary research units.}
\resumeItem{Delivered interactive, publication-ready analytical dashboards utilizing \textbf{Power BI} and \textbf{R Markdown} to synthesize complex health data, directly supporting stakeholders in the execution of peer-reviewed studies.}
\resumeItemListEnd

\resumeSubheading
      {Front End Developer Intern}{May 2024 -- Aug. 2024}
      {BERL}{}
\resumeItemListStart
\resumeItem{Architected highly responsive front-end applications by refactoring legacy \textbf{React} layouts, utilizing \textbf{CSS Flexbox/Grid}, and extending \textbf{Cascade CMS} templates, significantly reducing system latency and streamlining digital content delivery.}
\vspace{-4pt} 
\resumeItem{Transformed monolithic administrative interfaces into streamlined operational workflows while enforcing strict accessibility and code quality standards through rigorous peer code reviews, ensuring \textbf{continuous improvement}, high-performance UI deployments, and system stability.}
\resumeItemListEnd

\resumeSubheading
  {\href{}{Software Developer Intern}}{Sept 2023 -- Apr. 2024}
  {Cultureplex}{}
\resumeItemListStart
\resumeItem{Engineered custom \textbf{Python (pandas, NumPy)} and \textbf{SQL}-based analytical frameworks to process and aggregate complex datasets, accelerating large-scale data extraction for digital humanities research initiatives.}
\resumeItem{Optimized \textbf{PostgreSQL} database architecture through advanced \textbf{data modeling}, schema normalization, and strategic query tuning, mitigating performance bottlenecks and significantly reducing data retrieval latency.}
\resumeItem{Introduced a novel \textbf{ETL pipeline} leveraging \textbf{Python} and \textbf{LLMs (Generative AI)} to systematically \textbf{transform} unstructured text into structured formats, enabling seamless tool adoption by \textbf{cross-functional} research teams.}
\resumeItem{Generated high-impact visualizations (\textbf{Matplotlib/Seaborn}), translating complex aggregated data into unified \textbf{Excel/CSV} structures to support stakeholders in accelerating academic publications.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-------
\section{\textcolor{blue}{\textbf{Projects} $|$ \textnormal{\href{https://danielpark.vercel.app/}{\textcolor{blue}{\underline{\textnormal{View All}}} }}}} 

\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Spellchecker Application} $|$ \emph{Java, Java Swing}}{}
\resumeItemListStart
\resumeItem{Developed a standalone \textbf{Java Swing} desktop application for \textbf{spellchecking text documents}; implemented file handling and integrated a \textbf{Trie data structure} for efficient word storage and fast lookups.}
\resumeItem{Collaborated on project specifications and optimized \textbf{UI/UX design} to deliver a user-focused, high-performing solution with reliable text processing and responsive error detection.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{\textcolor{blue}{\textbf{Technical Skills \& Certifications}}}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \textbf{Data Science \& ML}{: Python, R, PyTorch, TensorFlow, Scikit-Learn, XGBoost, LLMs / Generative AI, Pandas, NumPy, Polars, SciPy, PySpark, Matplotlib, Seaborn, SHAP, UMAP, Yellowbrick, Jupyter} \\
    \textbf{Languages \& Web}{: SQL, Java, C, C++, C\#, Bash, PHP, HTML/CSS, XML, Django, .NET, React} \\
    \textbf{Cloud, Data Engineering \& DevOps}{: ETL / ELT, Data Pipelines, Data Modeling, Airflow, AWS, Azure, GCP, Docker, Git, Maven, Elasticsearch, Lucene, MapReduce, Regex, Excel, CSV, Claude Code} \\
    \textbf{Databases}{: MySQL, DynamoDB, Snowﬂake, Hadoop, Firebase, MongoDB, SQLite, PostgreSQL, MSSQL}
    }}
\end{itemize}

\resumeItemListStart
\vspace{-12pt}
  \resumeItem{\textbf{AWS} Machine Learning Engineer Certificate - In Progress}
  \vspace{-4pt}
  \resumeItem{\textbf{Meta} Backend Developer Specialization Certificate}
\resumeItemListEnd
\end{document}
